Cybersecurity Education and Accreditation:\\A Case Study of the UK

### 2019-06-22 FIE2019-final-TPJHD.tex
Tidied comments on knowledge

@@

% TC: other cyber breach examples here? e.g. Talktalk, Experian, madison dating thing, military examples?
Cybersecurity has increasingly been in the news over recent years, generally prompted by spectacular breaches, such as~\cite{BritishAirways2018a}. It needs attention across the spectrum \cite{Hannigan2019a}\footnote{Former Director of GCHQ: British equivalent of NSA.}:
\begin{quote}
``{\emph{...change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation.}}''
\end{quote}
\noindent
These global cybersecurity crises have compelled academic institutions to address the demand for educated cybersecurity professionals~\cite{McGettrick2013}. As no shared framework for ``cybersecurity'' as an academic discipline exists, growth has been unfocused and driven by training materials, which make it harder to create a common body of knowledge. An international perspective is still harder, as different nations use different criteria to define local needs~\cite{schneider2013}. As a result, new programmes entering this space are on their own to conceptualise, design, package and market their programs, as there is no globally accepted reference model for cybersecurity to allow employers or students to understand the extent of a given cybersecurity program~\cite{conklin-et-al:2014,Parrishetal2018a}.

>>>>

We demonstrate the positive effect that accreditation requirements can have, and give some recommendations both for research and for curriculum developments.

@@

% TC: other cyber breach examples here? e.g. Talktalk, Experian, madison dating thing, military examples?
Cybersecurity has increasingly been in the news over recent years, generally prompted by spectacular breaches, such as~\cite{BritishAirways2018a}. It needs attention across the spectrum \cite{Hannigan2019a}\footnote{Former Director of GCHQ: British equivalent of NSA.}:
\begin{quote}
``{\emph{...change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation.}}''
\end{quote}
\noindent
These global cybersecurity crises have compelled academic institutions to address the demand for educated cybersecurity professionals~\cite{McGettrick2013}. As no shared framework for ``cybersecurity'' as an academic discipline exists, growth has been unfocused and driven by training materials, which make it harder to create a common body of knowledge (\cite{Bristol2019a} is still a work in progress). An international perspective is still harder, as different nations use different criteria to define local needs~\cite{schneider2013}. As a result, new programmes entering this space are on their own to conceptualise, design, package and market their programs, as there is no globally accepted reference model for cybersecurity to allow employers or students to understand the extent of a given cybersecurity program~\cite{conklin-et-al:2014,Parrishetal2018a}.
